---
title       : Aging and Private Label Use
subtitle    : Preliminary Results
author      : Richards, Ramona, Gr8Dane
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
--- &basic1


```{r set.global.options, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(comment = NA, echo=F, results = 'asis', tidy = F, message = F)
```


```{r external.code}
chunk.dir <- 'D:\\research\\pl\\pl\\chunks\\'
read_chunk(paste(chunk.dir,"chunks_B.R",sep=""))
read_chunk(paste(chunk.dir,"chunks_presentation.R",sep=""))
```

```{r load.libraries.pres}
```

```{r functions.for.presentation}
```

```{r load.mcmc.run}
```

```{r read.effects}
```


### Model: 1st Stage

- We explain variation in PL share across (household,category) combinations.
- The model is 
$$
{\rm E}[s|X] = {\rm E}[s|X, s > 0] \times {\rm Pr}(s > 0|X),
$$
where X is household demographics and s is PL share.
- The first term on the right captures intensity of PL use for PL users, while the second term is the probability of being a PL user given X.
- The first expectation is computed as the expected value of 
$$
s \equiv \frac{\exp(y)}{1+\exp(y)},~~y=X'\beta + \varepsilon
$$
- The probability is modelled as a logit

--- &basic1

### Model: 2nd Stage

- We let $\beta$ and ${\rm Var}[\varepsilon]$ vary by category.
- We model variation in $\beta$ as 
$$
\beta_{cj} \sim {\rm N}(\pi_j + \pi^m_j D_c^m, \tau_j),\qquad j=1,\dots,K,
$$
where $D_c^m=1$ if category c is a medicine category.

--- &basic1

### Model: Demographics 

The following results are based on including the following demographics: 

- Number of purchases 
- Years in panel
- Income
- Education
- Household Structure (Male, Female, Joint)
- Age x Household Structure 

--- &basic1

### Data: Sample Size

```{r make.ggpl.sample.size1}
```

<div id ="chart1"></div>
```{r}
pl1$print('chart1',include_assets=TRUE, cdn = T)
```



